Online Laterality Battery Pre-Processing - short version

### 2020-11-20 battery-preprocessing_v6_DB.Rmd
original preprocess to make split half

```{r demograhics, warning=FALSE}
#Reading from OSF - this only works if files are public
demo_dat <- read.csv('https://osf.io/7smj6/download',stringsAsFactors = F)

@@

```{r sightednesss, warning=FALSE}
porta_dat <- read.csv("https://osf.io/zmqkt/download",stringsAsFactors = F)
miles_dat <-  read.csv("https://osf.io/ekqsp/download",stringsAsFactors = F)

@@

```{r EHI, warning=FALSE}
EHI <- read.csv("https://osf.io/kfdma/download",stringsAsFactors = F)

@@

eplot<-ggplot(allsum, aes(handpch,index_EHI, colour=gender)) +
  geom_jitter(wsubjectth=.25,height=2)+
  ggtitle("Handedness index on the Edinburgh Handedness Inventory")
eplot
#This is not perfect, but gives and subjectea to check EHI is valid etc.

ggplot(allsum, aes(x=index_EHI)) + geom_density(aes(group=handpch,fill=handpch))

@@

```{r lexTALE, warning=FALSE}
# read data
lexTALE <- read.csv("https://osf.io/h4btp/download",stringsAsFactors = F)

@@

# now create a data frame only for index 
lexTALE <- select(lexTale_score, "subject", "lexTALE")
# now merge with allsum
allsum <- merge(allsum, lexTALE, by= "subject")
# now write the full allsum 
write.csv(allsum, file = "./allsum_out.csv")

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "https://osf.io/mhk29/download" #day 1 data

  if (d ==2){
    data_file <-  "https://osf.io/ebm6s/download"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
chimdatL1<-select(filter(chim_dat1,side=='Left'),subject,accurate)
chimdatR1<-select(filter(chim_dat1,side=='Right'),subject,accurate)
chimdatL2<-select(filter(chim_dat2,side=='Left'),subject,accurate)
chimdatR2<-select(filter(chim_dat2,side=='Right'),subject,accurate)

@@

```{r dosummarydich}
includesubs <- which(allsum$exclude<2) #only plot/t-test included cases
origdat <- DL_dat1[DL_dat1$subject %in% includesubs,]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 1'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2
origdat <-  DL_dat2[DL_dat2$subject %in% includesubs,]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
```
```{r add.dichotic.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
DLdatL1<-select(filter(DL_dat1,side=='Left'),subject,accurate)
DLdatR1<-select(filter(DL_dat1,side=='Right'),subject,accurate)
DLdatL2<-select(filter(DL_dat2,side=='Left'),subject,accurate)
DLdatR2<-select(filter(DL_dat2,side=='Right'),subject,accurate)

@@

@@

```{r add.rdt.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
RDTdatL1<-select(filter(RDT_df1,side=='left'),subject,RT)
RDTdatR1<-select(filter(RDT_df1,side=='right'),subject,RT)
RDTdatL2<-select(filter(RDT_df2,side=='left'),subject,RT)
RDTdatR2<-select(filter(RDT_df2,side=='right'),subject,RT)

@@

origdat <- finger.long
measure <- '2sd'
origdat$X1 <- origdat$`2sd` #we used a dummy column name X1, so we can vary the data that are used in the pirate plot etc
task <- 'day 2sd'
dopirate(origdat,task,measure)
```
```{r add.fingerL_R}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
fingerL1<-select(finger.df,subject,L1)
fingerR1<-select(finger.df,subject,R1)
fingerL2<-select(finger.df,subject,L2)
fingerR2<-select(finger.df,subject,R2)

@@

@@

```{r lister}
# CF
day2.CF <- data.frame(matrix(nrow=length(complete.day2.CF), ncol= 2))
  colnames(day2.CF) <- c("task", "subject")
  day2.CF$subject <- complete.day2.CF
  day2.CF$task <- "CF"
# DL
day2.DL <- data.frame(matrix(nrow=length(complete.day2.DL), ncol= 2))
  colnames(day2.DL) <- c("task", "subject")
  day2.DL$subject <- complete.day2.DL
  day2.DL$task <- "DL"
# RD
day2.RD <- data.frame(matrix(nrow=length(complete.day2.RD), ncol= 2))
  colnames(day2.RD) <- c("task", "subject")
  day2.RD$subject <- complete.day2.RD
  day2.RD$task <- "CF"
# Finger
day2.FT <- data.frame(matrix(nrow=length(complete.day2.FT), ncol= 2))
  colnames(day2.FT) <- c("task", "subject")
  day2.FT$subject <- complete.day2.FT
  day2.FT$task <- "CF"
# now create a combined df
complete.day2a <- merge(day2.CF, day2.DL, by= "subject")
complete.day2b <- merge(day2.RD, day2.FT, by= "subject")
complete.day2 <- merge(complete.day2a, complete.day2b, by= "subject")
# add row to code
complete.day2$day2.complete <- 1
complete.day2 <- select(complete.day2, -2, -3, -4, -5)
# now merge into allsum
allsum <- merge(allsum, complete.day2, by= "subject", all= TRUE)

@@

  # write to data 
  myrow.2 <- myrow.2+1
  CF.corrs$trial[myrow.2] <- y
  CF.corrs$cor[myrow.2] <- move_corr
}
# plot
CF.corrs <- na.omit(CF.corrs)
CF.cor.plot <- ggplot(CF.corrs, aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "blue") +
  geom_hline(yintercept=.75, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("B") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(CF.corrs[CF.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(CF.corrs[CF.corrs$cor >= .75,]$trial)))
}
```

@@

  # write to data 
  myrow.2 <- myrow.2+1
  DL.corrs$trial[myrow.2] <- y
  DL.corrs$cor[myrow.2] <- move_corr
}
# plot
DL.corrs <- na.omit(DL.corrs)
DL.cor.plot <- ggplot(DL.corrs, aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "blue") +
  geom_hline(yintercept=.75, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("A") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(DL.corrs[DL.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(DL.corrs[DL.corrs$cor >= .75,]$trial)))
}

all.cor.plot <- suppressMessages(suppressWarnings(ggpubr::ggarrange(DL.cor.plot, CF.cor.plot)))
all.cor.plot
# save
ggsave(
  "all.cor.plot.png",
  plot = all.cor.plot,
  width = 6, height = 3,
  dpi = 300
)
```

>>>>

```{r demograhics, warning=FALSE}
#Reading from OSF - this only works if files are public
#demo_dat <- read.csv('https://osf.io/7smj6/download',stringsAsFactors = F)
demo_dat <- read.csv("./data/Demographics.csv",stringsAsFactors = F)

@@

```{r sightednesss, warning=FALSE}
#porta_dat <- read.csv("https://osf.io/zmqkt/download",stringsAsFactors = F)
#miles_dat <-  read.csv("https://osf.io/ekqsp/download",stringsAsFactors = F)
porta_dat <- read.csv("./data/porta.csv",stringsAsFactors = F)
miles_dat <- read.csv("./data/miles.csv",stringsAsFactors = F)

@@

```{r EHI, warning=FALSE}
#EHI <- read.csv("https://osf.io/kfdma/download",stringsAsFactors = F)
EHI <- read.csv("./data/EHI.csv",stringsAsFactors = F)

@@

eplot<-ggplot(allsum, aes(handpch,index_EHI, colour=gender)) +
  geom_jitter(wsubjectth=.25,height=2)+
  ggtitle("Handedness index on the Edinburgh Handedness Inventory")
eplot
#This is not perfect, but gives and subjectea to check EHI is valid etc.
allsum$handpch <- as.factor(allsum$handpch)
ggplot(allsum, aes(x=index_EHI)) + geom_density(aes(group=handpch,fill=handpch))

@@

```{r lexTALE, warning=FALSE}
# read data
#lexTALE <- read.csv("https://osf.io/h4btp/download",stringsAsFactors = F)
lexTALE <- read.csv("./data/LexTALE.csv",stringsAsFactors = F)

@@

# now create a data frame only for index 
lexTALE <- dplyr::select(lexTale_score, "subject", "lexTALE")
# now merge with allsum
allsum <- merge(allsum, lexTALE, by= "subject")
# now write the full allsum 
write.csv(allsum, file = "./allsum_out.csv")

@@

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "./data/combined/day1_combined.csv" #"https://osf.io/mhk29/download" #day 1 data

  if (d ==2){
    data_file <-  "./data/combined/day2_combined.csv"#"https://osf.io/ebm6s/download"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
chimdatL1<-dplyr::select(filter(chim_dat1,side=='Left'),subject,accurate)
chimdatR1<-dplyr::select(filter(chim_dat1,side=='Right'),subject,accurate)
chimdatL2<-dplyr::select(filter(chim_dat2,side=='Left'),subject,accurate)
chimdatR2<-dplyr::select(filter(chim_dat2,side=='Right'),subject,accurate)

@@

```{r dosummarydich}
includesubs <- which(allsum$exclude<2) #only plot/t-test included cases
origdat <- DL_dat1[DL_dat1$subject %in% includesubs,]
measure <- 'Accuracy'
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 1'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
t.test(origdat$accurate~ origdat$side)
#Now repeat for day 2
origdat <-  DL_dat2[DL_dat2$subject %in% includesubs,]
origdat$X1 <- origdat$accurate #we used a dummy column name so we can vary the data that are used in the pirate plot etc
task <- 'Dichotic listening day 2'
measure <- 'Accuracy'
dopirate(origdat,task,measure)
origdat$X1 <- origdat$RT
measure <- 'RT'
dopirate(origdat,task,measure)
```
```{r add.dichotic.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
DLdatL1<-dplyr::select(filter(DL_dat1,side=='Left'),subject,accurate)
DLdatR1<-dplyr::select(filter(DL_dat1,side=='Right'),subject,accurate)
DLdatL2<-dplyr::select(filter(DL_dat2,side=='Left'),subject,accurate)
DLdatR2<-dplyr::select(filter(DL_dat2,side=='Right'),subject,accurate)

@@

#Also record % correct for each category in allsum
for (d in 1:2){
  myfile<-RDT_df1
  if(d==2){ myfile<-RDT_df2}
pcorL<-myfile[myfile$side=='left',]
pcorR<- myfile[myfile$side=='right',]
pcorNull <- myfile[myfile$side=='no rhyme',]
pcorL<-dplyr::select(pcorL,subject,p.corr)
pcorR<-dplyr::select(pcorR,subject,p.corr)
pcorNull<-dplyr::select(pcorNull,subject,p.corr)
colnames(pcorL)[2]<-paste0('RDT',d,'.pcorrL')
colnames(pcorR)[2]<-paste0('RDT',d,'.pcorrR')
colnames(pcorNull)[2]<-paste0('RDT',d,'.pcorrNull')
allsum <- merge(allsum,pcorL,by="subject")
allsum <- merge(allsum,pcorR,by="subject")
allsum <- merge(allsum,pcorNull,by="subject")
}

@@

```{r add.rdt.raw}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
RDTdatL1<-dplyr::select(filter(RDT_df1,side=='left'),subject,RT)
RDTdatR1<-dplyr::select(filter(RDT_df1,side=='right'),subject,RT)
RDTdatL2<-dplyr::select(filter(RDT_df2,side=='left'),subject,RT)
RDTdatR2<-dplyr::select(filter(RDT_df2,side=='right'),subject,RT)

@@

origdat <- finger.long
measure <- '2sd'
origdat$X1 <- origdat$`2sd` #we used a dummy column name X1, so we can vary the data that are used in the pirate plot etc
task <- 'day 2sd'
dopirate(origdat,task,measure)
```
```{r add.fingerL_R}
#added by DB 17th July 2020: include raw accuracy L and R in the allsum dataframe
fingerL1<-dplyr::select(finger.df,subject,L1)
fingerR1<-dplyr::select(finger.df,subject,R1)
fingerL2<-dplyr::select(finger.df,subject,L2)
fingerR2<-dplyr::select(finger.df,subject,R2)

@@

### Calculate split half reliability

```{r Chimeric Split Half}
varlist <-   c("subject", "side", "accurate", "RT") #need to be in this order, ie sub, side, acc and RR
latlist <- c("Left","Right") #names of factor levels
nloop=2 #same as levels of latlist
# create data frames
CF_dat1$split <- c("odds", "even")
  CF_dat_1.1 <- CF_dat1[CF_dat1$split== "odds",]
  CF_dat_1.2 <- CF_dat1[CF_dat1$split== "even",]
CF_dat2$split <- c("odds", "even")
  CF_dat_2.1 <- CF_dat2[CF_dat2$split== "odds",]
  CF_dat_2.2 <- CF_dat2[CF_dat2$split== "even",]
# create aggregate data
chim_dat1.1 <- make.df(CF_dat_1.1,varlist,latlist,nloop)
chim_dat1.2 <- make.df(CF_dat_1.2,varlist,latlist,nloop)
chim_dat2.1 <- make.df(CF_dat_2.1,varlist,latlist,nloop)
chim_dat2.2 <- make.df(CF_dat_2.2,varlist,latlist,nloop)
#exclude
#find included cases
w<-which(allsum$exclude==0)
  inclsubs <- allsum$subject[w]

# NOW MAKE LI_z
# 1 odds
task<-'Chimeric faces'
origdat<-chim_dat1.1
origdat$X1 <- origdat$N
mycolname<-"split.chim.1.1"
mycutoff <- 10 #NB! need to check against prereg. I think this is N correct, rather than percentage. People with avg scores below this value will be excluded.
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# 1 even
origdat<-chim_dat1.2
origdat$X1 <- origdat$N
mycolname<-"split.chim.1.2"
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# 2 odds
origdat<-chim_dat2.1
origdat$X1 <- origdat$N
mycolname<-"split.chim.2.1"
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# 2 evens
origdat<-chim_dat2.2
origdat$X1 <- origdat$N
mycolname<-"split.chim.2.2"
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# remove
w<-which(allsum$exclude == 1)
  allsum$split.chim.1.1[w] <- NA
  allsum$split.chim.1.2[w] <- NA
  allsum$split.chim.2.1[w] <- NA
  allsum$split.chim.2.2[w] <- NA

print(paste0("Chimeric faces session 1 split-half: ", cor(allsum$split.chim.1.1, allsum$split.chim.1.2, use = "complete.obs")))
print(paste0("Chimeric faces session 2 split-half: ", cor(allsum$split.chim.2.1, allsum$split.chim.2.2, use = "complete.obs")))
```

```{r Dichotic Split Half}
varlist <-   c("subject", "side", "accurate", "RT") #need to be in this order, ie sub, side, acc and RR
origdat <- dichotic_dat1
latlist <- c("Left","Right") #names of factor levels
nloop=2 #same as levels of latlist
# made data frames
dichotic_dat1$split <- c("odds", "even")
  DL_1.1 <- dichotic_dat1[dichotic_dat1$split== "odds",]
  DL_1.2 <- dichotic_dat1[dichotic_dat1$split== "even",]
dichotic_dat2$split <- c("odds", "even")
  DL_2.1 <- dichotic_dat2[dichotic_dat2$split== "odds",]
  DL_2.2 <- dichotic_dat2[dichotic_dat2$split== "even",]
# create aggregate data
DL_dat1.1 <- make.df(DL_1.1,varlist,latlist,nloop)
DL_dat1.2 <- make.df(DL_1.2,varlist,latlist,nloop)
DL_dat2.1 <- make.df(DL_2.1,varlist,latlist,nloop)
DL_dat2.2 <- make.df(DL_2.2,varlist,latlist,nloop)
# exclude
w<-which(is.na(DL_dat1.1$subject))
  if (length(w)>0) {DL_dat1.1<-DL_dat1.1[-w,]}
w<-which(is.na(DL_dat1.2$subject))
  if (length(w)>0) {DL_dat1.2<-DL_dat1.2[-w,]}
w<-which(is.na(DL_dat2.1$subject))
  if (length(w)>0) {DL_dat2.1<-DL_dat2.1[-w,]}
w<-which(is.na(DL_dat2.2$subject))
  if (length(w)>0) {DL_dat2.2<-DL_dat2.2[-w,]}
DL_dat1.1[is.na(DL_dat1.1)] <- 0
DL_dat1.2[is.na(DL_dat1.2)] <- 0
DL_dat2.1[is.na(DL_dat2.1)] <- 0
DL_dat2.2[is.na(DL_dat2.2)] <- 0

# MAKE Z SCORE
# day 1 odds
task<-'Dichotic listening'
origdat<-DL_dat1.1
origdat$X1 <- origdat$N
mycolname<-"split.DL.1.1"
mycutoff <- 10 #NB! need to check against prereg. I think this is N correct, rather than percentage. People with avg scores below this value will be excluded.
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# day 1 evens
origdat<-DL_dat1.2
origdat$X1 <- origdat$N
mycolname<-"split.DL.1.2"
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# day 2 odds
origdat<-DL_dat2.1
origdat$X1 <- origdat$N
mycolname<-"split.DL.2.1"
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
# day 2 evens
origdat<-DL_dat2.2
origdat$X1 <- origdat$N
mycolname<-"split.DL.2.2"
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)
#remove
# remove
w<-which(allsum$exclude == 2)
  allsum$split.DL.1.1[w] <- NA
  allsum$split.DL.1.2[w] <- NA
  allsum$split.DL.2.1[w] <- NA
  allsum$split.DL.2.2[w] <- NA

print(paste0("Dichotic listening session 1 split-half: ", cor(allsum$split.DL.1.1, allsum$split.DL.1.2, use = "complete.obs")))
print(paste0("Dichotic listening session 2 split-half: ", cor(allsum$split.DL.2.1, allsum$split.DL.2.2, use = "complete.obs")))
```

#### Rhyme decision task

```{r Rhyme Split Half}
varlist <-   c("subject", "side", "accurate", "RT") #need to be in this order, ie sub, side, acc and RR
latlist <- c("left","no rhyme","right") #names of factor levels
nloop<-length(latlist)
# made data frames
RDT_dat1$split <- c("odds", "even")
  RDT_dat1.1 <- RDT_dat1[RDT_dat1$split== "odds",]
  RDT_dat1.2 <- RDT_dat1[RDT_dat1$split== "even",]
RDT_dat2 <- RDT_dat2[-nrow(RDT_dat2),]
RDT_dat2$split <- c("odds", "even")
  RDT_dat2.1 <- RDT_dat2[RDT_dat2$split== "odds",]
  RDT_dat2.2 <- RDT_dat2[RDT_dat2$split== "even",]
# create aggregate data
RDT_df1.1 <- make.df(RDT_dat1,varlist,latlist,nloop)
RDT_df1.2 <- make.df(RDT_dat2,varlist,latlist,nloop)
RDT_df2.1 <- make.df(RDT_dat1,varlist,latlist,nloop)
RDT_df2.2 <- make.df(RDT_dat2,varlist,latlist,nloop)
# remove NaN
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))
RDT_df1.1[is.nan(RDT_df1.1)] <- NA
RDT_df1.2[is.nan(RDT_df1.2)] <- NA
RDT_df2.1[is.nan(RDT_df2.1)] <- NA
RDT_df2.2[is.nan(RDT_df2.2)] <- NA

# exclude
wn <-unique(which(RDT_df1.1$accurate ==0),which(RDT_df1.2$accurate ==0, (which(RDT_df2.1$accurate ==0, (which(RDT_df2.2$accurate ==0))))))
w1<-which(RDT_df1.1$p.corr < 75)
w2<-which(RDT_df1.2$p.corr < 75)
w3<-which(RDT_df2.1$p.corr < 75)
w4<-which(RDT_df2.2$p.corr < 75)
exRDT<-unique(c(RDT_df1.1$subject[w1],
                RDT_df1.2$subject[w2],
                RDT_df2.1$subject[w3],
                RDT_df2.1$subject[w4],
                RDT_df1.1$subject[wn],
                RDT_df1.2$subject[wn],
                RDT_df2.1$subject[wn],
                RDT_df2.2$subject[wn]))
allsum$exRDT_split <- 0
allsum$exRDT_split[allsum$subject %in% exRDT]<-1 #decided best to have separate column for exclusion for each task
w<-which(allsum$exRDT_split==0)  
incRDT <- allsum$subject[w]
ninc <- length(incRDT)

# MAKE Z LAT
for (d in 1:4){
  ifelse(d==1, myfile<-RDT_dat1.1, 
         ifelse(d==2, myfile<-RDT_dat1.2,
                ifelse(d==3, myfile<-RDT_dat2.1,
                       myfile<-RDT_dat2.2)))
    ifelse(d==1, lab<- 1.1, 
         ifelse(d==2, lab<- 1.2,
                ifelse(d==3, lab<- 2.1,
                       lab <- 2.2)))
  nsubs <- nrow(allsum)
  allsum$tempt<-NA #initialise a new column
  for (i in 1:nsubs) {
    mysub<-filter(myfile,side %in% c('left','right'),subject==allsum$subject[i])
    if(nrow(mysub)>10)
    {
      mymean<-aggregate(RT~side,mysub,FUN = mean)
      mysd<-aggregate(RT~side,mysub,FUN = sd)
        myN<-aggregate(RT~side,mysub,FUN = length)
      se1<-mysd[1,2]/sqrt(myN[1,2])
      se2<-mysd[2,2]/sqrt(myN[2,2])
      se<-sqrt(se1^2+se2^2)
      allsum$tempt[i]<-(mymean[1,2]-mymean[2,2])/se
    }
  }
  wc<-which(colnames(allsum)=='tempt')
  colnames(allsum)[wc]<-paste0('split.RDT.',lab)
}
w<-which(is.na(allsum$Day1.RDT_RT_LI)) #remove those with NA in LI
  allsum$split.RDT.1.1[w]<-NA
  allsum$split.RDT.1.2[w]<-NA
w<-which(is.na(allsum$Day2.RDT_RT_LI))
  allsum$split.RDT.2.1[w]<-NA
  allsum$split.RDT.2.1[w]<-NA

print(paste0("Rhyme decision session 1 split-half: ", cor(allsum$split.RDT.1.1, allsum$split.RDT.1.2, use = "complete.obs")))
print(paste0("Rhyme decision session 2 split-half: ", cor(allsum$split.RDT.2.1, allsum$split.RDT.2.2, use = "complete.obs")))
```

@@

```{r lister}
# CF
day2.CF <- data.frame(matrix(nrow=length(complete.day2.CF), ncol= 2))
  colnames(day2.CF) <- c("task", "subject")
  day2.CF$subject <- complete.day2.CF
  day2.CF$task <- "CF"
# DL
day2.DL <- data.frame(matrix(nrow=length(complete.day2.DL), ncol= 2))
  colnames(day2.DL) <- c("task", "subject")
  day2.DL$subject <- complete.day2.DL
  day2.DL$task <- "DL"
# RD
day2.RD <- data.frame(matrix(nrow=length(complete.day2.RD), ncol= 2))
  colnames(day2.RD) <- c("task", "subject")
  day2.RD$subject <- complete.day2.RD
  day2.RD$task <- "CF"
# Finger
day2.FT <- data.frame(matrix(nrow=length(complete.day2.FT), ncol= 2))
  colnames(day2.FT) <- c("task", "subject")
  day2.FT$subject <- complete.day2.FT
  day2.FT$task <- "CF"
# now create a combined df
complete.day2a <- merge(day2.CF, day2.DL, by= "subject")
complete.day2b <- merge(day2.RD, day2.FT, by= "subject")
complete.day2 <- merge(complete.day2a, complete.day2b, by= "subject")
# add row to code
complete.day2$day2.complete <- 1
complete.day2 <- dplyr::select(complete.day2, -2, -3, -4, -5)
# now merge into allsum
allsum <- merge(allsum, complete.day2, by= "subject", all= TRUE)

@@

  # write to data 
  myrow.2 <- myrow.2+1
  CF.corrs$trial[myrow.2] <- y
  CF.corrs$cor[myrow.2] <- move_corr
}
# plot
CF.corrs <- na.omit(CF.corrs)
CF.cor.plot <- ggplot(CF.corrs, aes(x=trial, y=abs(cor))) +
  geom_hline(yintercept=.65, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_bw() +
  xlab("Number of trials") + ylab("Test-retest reliability") + ggtitle("(B)") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(CF.corrs[CF.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(CF.corrs[CF.corrs$cor >= .75,]$trial)))
}
```

@@

  # write to data 
  myrow.2 <- myrow.2+1
  DL.corrs$trial[myrow.2] <- y
  DL.corrs$cor[myrow.2] <- move_corr
}
# plot
DL.corrs <- na.omit(DL.corrs)
DL.cor.plot <- ggplot(DL.corrs, aes(x=trial, y=abs(cor))) +
  geom_hline(yintercept=.65, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_bw() +
  xlab("Number of trials") + ylab("Test-retest reliability") + ggtitle("(A)") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(DL.corrs[DL.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(DL.corrs[DL.corrs$cor >= .75,]$trial)))
}

all.cor.plot <- suppressMessages(suppressWarnings(ggpubr::ggarrange(DL.cor.plot, CF.cor.plot)))
all.cor.plot
# save
ggsave(
  "./plots/all.cor.plot.png",
  plot = all.cor.plot,
  width = 6, height = 3,
  dpi = 300
)
```
